\documentclass[11pt, a4paper]{moderncv}

\moderncvstyle{classic}
\moderncvcolor{grey}
\usepackage[scale=0.75]{geometry}
\usepackage[T1]{fontenc}
\usepackage{palatino}

\name{Petro}{Ravlinko}
\title{Senior Software Engineer}
\phone[mobile]{+38~(093)~148~72~81}
\email{petro.ravlinko@gmail.com}
\quote{Decisions must be goal-based to meet expectations.\newline{}A high-automation level of the delivery process can provide the most predictable lead time of changes. The leadership should go from heart to be efficient and proficient, everything is negotiable with enough information.\newline{}\newline{}\newline{}You can use the brilliant but lazy man as a strategist. @General Douglas MacArthur}


\begin{document}
\makecvtitle

\section{Experience}
\subsection{Vocational}
\cventry{2020--2022}{Senior Software Engineer}{Intent Solution Group Inc.}{Lviv}{}
{Engineering Lead.\newline{}Detailed achievements:
\begin{itemize}
\item Develop practices for Engineering:
\begin{itemize}
\item Java PDP matrix
\item Architecture reviews and proposals
\item AWS Serverless Enterprise CI/CD
\end{itemize}
\item Review and introduce engineering best practices implementation;
\item Implementation of the best practices;
\item Code review for Java/IaC projects.
\item Consult Team Leaders with technical tasks
\item Share team management triks and SCRUM best practices
\item Adopted AWS technologies:
\begin{itemize}
\item Lambdas/S3/ECS(Fargate)/SQS/Cognito/Directory/IAM/CloudFront
\item AWS Serverless Enterprise CI/CD (CodeBuild, Codepipeline (GitHub/S3/ECS/ECR Actions))
\item IoC CloudFormation(YAML)
\end{itemize}
\item Faced issues:
\begin{itemize}
\item Planning efficiency
\item Early software quality feedback
\item Continuos improvement
\end{itemize}
\end{itemize}}

\cventry{2018--2020}{Senior Software Engineer}{SoftServe Inc.}{Lviv}{}
{Software Development Office (SDO) consulting expert in engineering.\newline{}Detailed achievements:
\begin{itemize}
\item Passed Software Solution Architecture ramp-up training and workshop;
\item Develop practices for Engineering Best Practices catalog:
\begin{itemize}
\item Developer testing
\item Technical debt management
\end{itemize}
\item Evaluation of projects on engineering best practices implementation;
\item Assistance for projects with the implementation of the best practice;
\item Code review for Java projects.
\end{itemize}}

\cventry{2017--2018}{Senior Software Engineer}{nextlevel.ai}{Lviv}{}
{Chatbots development and integration. Lead PoC Development process. Research and implement integration Intelligence System with different platforms. Design and estimate small software solutions.
\begin{itemize}
\item Technologies:
\begin{itemize}
\item Java SE, EE
\item Spring Boot, Framework, Data
\item Hippo CMS
\item Lombok
\item jUnit, Mockito, Spring Test, Cucmber-JVM, Rest-Assured, Serenity BDD  
\end{itemize}
\item Tools:
\begin{itemize}
\item Maven
\item GitLab 
\end{itemize}
\end{itemize}}

\cventry{2016--2017}{Middle Software Engineer}{Symphony Solutions}{Lviv}{}
{Develop and support services for gambling system. Regular team rotation. Follow Scrum and Kanban ceremonies, and TDD practice. 
\begin{itemize}
\item Technologies:
\begin{itemize}
\item Java SE, EE, JAX-RS Jersey
\item Spring Boot, Framework, Data
\item Lombok 
\item jUnit, Mockito, Spring Test
\end{itemize}
\item Tools:
\begin{itemize}
\item Apache Maven
\item Gradle
\item Atlassian Stash
\item Docker, docker-compose
\end{itemize}
\end{itemize}}

\cventry{2014--2016}{Middle Java Software Engineer}{EPAM Systems}{Lviv}{}
{E-commerce. Development of B2C and B2B services. Participate as a member in Scrum ceremonies. There were applied TDD, BDD, and Pair programming practices. Follow BDD way of feature discovery and formulation via Gherkin code, and cover the system with appropriate amount of unit and UI tests. Trunk-based delivery process with automated acceptance, system integration, and user acceptance stages.
\begin{itemize}
\item Technologies:
\begin{itemize}
\item Java SE, EE
\item Spring Framework
\item ZK Framework
\item SAP Hybris Commerce Platform
\item JavaScript
\item jUnit, Mockito, 
\item Gherkin, Cucumber-JVM, Selenium
\end{itemize}
\item Tools:
\begin{itemize}
\item Ant
\item GitLab
\end{itemize}
\end{itemize}}

\cventry{2013--2014}{Middle Software Engineer}{Optigra}{Lviv}{}
{Develop financial services for investment 360 system for customers of a bank in USA. As a member of the development team participate Scrum ceremonies and processes. Intense usage of SQL queries. Follows TDD principles.
\begin{itemize}
\item Technologies:
\begin{itemize}
\item Java SE, EE
\item Spring Framework
\item jUnit, Mockito
\item SQL
\end{itemize}
\item Tools:
\begin{itemize}
\item Eclipse
\item Maven
\item SVN
\end{itemize}
\end{itemize}}

\cventry{2011--2013}{Junior/Middle Java Software Engineer}{EPAM Systems}{Lviv}{}
{As a support engineer on the Java Web projects under maintenance and reconstruction, I was responsible for fixing of risen bugs, implementing requested changes on a service and client sides, and covering code with unit tests, according to established processes.
\begin{itemize}
\item Technologies:
\begin{itemize}
\item Java SE, EE
\item Spring Framework
\item JBoss Seem
\item jUnit, Mockito
\item JavaScript, jQuery
\item SQL
\end{itemize}
\item Tools:
\begin{itemize}
\item Eclipse
\item Ant
\item Maven
\item SVN
\item Git
\end{itemize}
\end{itemize}}


\section{Education}
\cventry{2010--2011}{Master}{ICTAM}{Lviv Polytechnic National University}{\textit{Computer Systems and Networks}}
{}
\cventry{2006--2010}{Bachelor}{ICTAM}{Lviv Polytechnic National University}{\textit{Computer Engineering}}
{}



\section{Certification}
\cventry{2019--2021}{Google Cloud}{Professional Cloud Architect}{Credential ID 13500247}{}
{Credential URL https://www.credential.net/lvuqh9to}
\cventry{2021--2024}{AWS}{AWS Certified Developer - Associate}{Validation Number DPH2THXLJN1E1P93}{}
{Validate at: http://aws.amazon.com/verification}

\section{Languages}
\cvitemwithcomment{Ukrainian}{Native}{}
\cvitemwithcomment{English}{Intermediate}{B2}
\cvitemwithcomment{Spanish}{Elementary}{A1}
\end{document}
